\documentclass[11pt,a4paper]{scrartcl}

% Support for UTF-8 and non-English letters require the following two
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% Font packages
\usepackage[default,defaultsans,oldstyle,proportional]{lato}
\usepackage[scaled]{beramono}
\usepackage{sfmath}
% Optimized justification via improved microtypography on character level
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage[none]{hyphenat} % disable all hyphenation
\setlength{\emergencystretch}{3em} % allow extra hfill, needed if hyphenation disabled
%\overfullrule=1mm % mark overfull boxes
%\usepackage{showframe} % show edges of text areas
% Page layout
\usepackage[left=20mm,right=20mm,top=20mm,bottom=20mm,
   nohead,foot=10mm]{geometry}
% SVN metadata
\usepackage[today,revrange,nofancy]{svninfo}
\svnInfo $Id: minutes_week09.tex 6594 2023-05-04 14:10:03Z dfil0003 $
% Page headers
\usepackage{scrlayer-scrpage}
\usepackage{lastpage}
\usepackage{fancyvrb}
% Page header
\KOMAoptions{headsepline=0pt,plainheadsepline=off}
\ihead*{}
\chead*{}
\ohead*{}
% Page footer
\KOMAoptions{footsepline=0pt,plainfootsepline=off}
\ifoot*{Last edited: \svnMaxToday}
\cfoot*{Page \thepage{} of \pageref{LastPage}}
\ofoot*{Document v.\svnInfoMaxRevision}
% Text layout
\KOMAoption{parskip}{never}
\newlength{\myparindent}
\newlength{\myparskip}
\setlength{\myparindent}{0pt}
\setlength{\myparskip}{5pt plus 1pt}
\setparsizes{\myparindent}{\myparskip}{0.1\linewidth plus 1fil}
\RedeclareSectionCommand[beforeskip=6pt,afterskip=3pt,afterindent=false]{section}
\RedeclareSectionCommand[beforeskip=6pt,afterskip=-0.5em,afterindent=false]{paragraph}
\RaggedRight

% Meeting details
\title{Meeting Minutes -- Group 5}
\author{Location: 0 B 6}
\date{06 May 2023, 13:00--15:00}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Gabriel Apap (Chair),
Damjan Filipovic (Minutes),
Mark Mizzi 

\section*{Discussion}

\begin{enumerate}
\item Reading and approval of minutes from previous meeting
\begin{enumerate}
    \item Approved
\end{enumerate}

\item Matters arising from minutes
\begin{enumerate}
    \item On point 3 a of previous minutes it is thought that the SysTick timer code was interfering with the LCD driver code but debugging was inconclusive as the error was inconsistent.
\end{enumerate}

\item Discussion of timer code
\begin{enumerate}
    \item The \verb!timer_set_callback! function was modified to set the timer period and start the timer.
\end{enumerate}

\item Discussion of DAC code
\begin{enumerate}
    \item Two functions were defined, \verb!tone_init! and \verb!tone_play_or_enqueue!, which initializes the tone generation code and produces or en-queues the tone respectively. The \verb!tone_play_or_enqueue! function is very similar to the \verb!start_or_enqueue! function.
    \item The sine table is no longer hard coded but is generated using the \verb!sinewave_init()! function which is called with the \verb!tone_init! function.
    \item Since the timer code was changed, inter-symbol spacing was temporarily removed from the code. This was accomplished by having \verb!timer_callback_isr! immediately call \verb!pop_and_dac_interrupt_enable! when it is done generating the samples.
    \item The symbol length is specified in milliseconds. This allows for much finer control than earlier.
\end{enumerate}

\item Discussion of keypad code
\begin{enumerate}
    \item The rows and columns are initially set to a logic level of 1, with the columns being the output pins and the rows being set to pullup.
    \item The \verb!start_keypad! function loops over the columns, setting them to 0, and then reading the rows to detect the exact key pressed.
    \item Delays are added after the \verb!gpio_set! and the end of the outer loop to account for debouncing and spurious input.
\end{enumerate}

\item Assign work between team
\begin{enumerate}
    \item Inter-symbol spacing.
    \item Documentation.
    \item Implementation of LPF and debouncing.
    \item More permanent version of the circuits.
    \item Doing the keypad with interrupts.
    \item Bring back k (sampling frequency divider) from before.
    \item Settings.
    \item Getting a casing for the DMTF encoder.
\end{enumerate}

\item Other matters.
\begin{enumerate}
    \item Tasks not assigned during this meeting will be assigned the following one.
\end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

\item Inter-symbol spacing
\begin{flushright}
Assigned to: \textbf{Mark Mizzi} \\
Deadline: \textbf{Next meeting}
\end{flushright}

\item Documentation of timer and dac code, implementation of LPF and debouncing and sampling frequency divider.
\begin{flushright}
Assigned to: \textbf{Gabriel Apap} \\
Deadline: \textbf{Next meeting}
\end{flushright}

\item Documentation of keypad code, keypad with interrupts
\begin{flushright}
Assigned to: \textbf{Damjan Filipovic} \\
Deadline: \textbf{Next meeting}
\end{flushright}

% Add more actions as necessary

\end{enumerate}

\end{document}
