\documentclass[11pt,a4paper]{scrartcl}

% Support for UTF-8 and non-English letters require the following two
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% Font packages
\usepackage[default,defaultsans,oldstyle,proportional]{lato}
\usepackage[scaled]{beramono}
\usepackage{sfmath}
% Optimized justification via improved microtypography on character level
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage[none]{hyphenat} % disable all hyphenation
\setlength{\emergencystretch}{3em} % allow extra hfill, needed if hyphenation disabled
%\overfullrule=1mm % mark overfull boxes
%\usepackage{showframe} % show edges of text areas
% Page layout
\usepackage[left=20mm,right=20mm,top=20mm,bottom=20mm,
   nohead,foot=10mm]{geometry}
% SVN metadata
\usepackage[today,revrange,nofancy]{svninfo}
\svnInfo $Id: minutes_week06.tex 6875 2023-03-30 15:19:26Z mmiz0052 $
% Page headers
\usepackage{scrlayer-scrpage}
\usepackage{lastpage}
\usepackage{fancyvrb}
% Page header
\KOMAoptions{headsepline=0pt,plainheadsepline=off}
\ihead*{}
\chead*{}
\ohead*{}
% Page footer
\KOMAoptions{footsepline=0pt,plainfootsepline=off}
\ifoot*{Last edited: \svnMaxToday}
\cfoot*{Page \thepage{} of \pageref{LastPage}}
\ofoot*{Document v.\svnInfoMaxRevision}
% Text layout
\KOMAoption{parskip}{never}
\newlength{\myparindent}
\newlength{\myparskip}
\setlength{\myparindent}{0pt}
\setlength{\myparskip}{5pt plus 1pt}
\setparsizes{\myparindent}{\myparskip}{0.1\linewidth plus 1fil}
\RedeclareSectionCommand[beforeskip=6pt,afterskip=3pt,afterindent=false]{section}
\RedeclareSectionCommand[beforeskip=6pt,afterskip=-0.5em,afterindent=false]{paragraph}
\RaggedRight

% Meeting details
\title{Meeting Minutes -- Group 5}
\author{Location: 0 B 6}
\date{30 March 2023, 13:00--15:30}

\begin{document}

\maketitle

\section*{Present}
% Members actually present at the meeting
Mark Mizzi,
Damjan Filipovic,
Gabriel Apap (Chair)

\section*{Discussion}

\begin{enumerate}

   \item Reading and approval of minutes from previous meeting

   \item Matters arising from minutes
    \begin{enumerate}
        \item None
    \end{enumerate}
   
   \item Progress report from group members
      \begin{enumerate}
         \item Gabriel added the LCD driver code found in the labs in the project.

         \item Damjan lfinished writing the keypad code however, it still has some bugs.

         \item Mark fixed some bugs in the DAC interrupt code and documented the work.
      \end{enumerate}
   
   \item Test the core code developed.
      \begin{enumerate}
         \item The keypad was successfully soldered and connected to the microcontroller.
         \item The DAC interrupt and LCD code were confirmed to work, however the keypad code has some bugs that need to be fixed.
      \end{enumerate}
   
   \item Discuss documentation tasks.
      \begin{enumerate}
         \item No documentation to be done for the LCD as it is already documented.
         \item Mark will be updating the design brief with details about the newly added DAC interrupt code.
         \item Damjan will be documenting the keypad code (using Doxygen) once the bugs are fixed.
      \end{enumerate}
   
   \item Discuss potential research tasks (e.g. persistent storage).
      \begin{enumerate}
         \item Gabriel may have time to start researching the persistent storage driver during the holidays.
         \item Mark and Damjan will be looking at refactoring the already existing code.
      \end{enumerate}
   
   \item Other matters.
      \begin{enumerate}
         \item No other matters.
      \end{enumerate}

\end{enumerate}

\section*{Actions}

\begin{enumerate}

\item Update the design brief and assist Damjan in refactoring the existing code.
\begin{flushright}
Assigned to: \textbf{Mark Mizzi} \\
Deadline: \textbf{Next meeting}
\end{flushright}

\item Research the persistent storage driver.
\begin{flushright}
Assigned to: \textbf{Gabriel Apap} \\
Deadline: \textbf{Next meeting}
\end{flushright}

\item Fix and document keypad code.
\begin{flushright}
Assigned to: \textbf{Damjan Filipovic} \\
Deadline: \textbf{Next meeting}
\end{flushright}

% Add more actions as necessary

\end{enumerate}

\end{document}
