\documentclass[11pt,a4paper,twocolumn]{scrartcl}

% Support for UTF-8 and non-English letters require the following two
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
% Font packages
\usepackage[default,defaultsans,oldstyle,proportional]{lato}
\usepackage[scaled]{beramono}
\usepackage{sfmath}
% Optimized justification via improved microtypography on character level
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage[none]{hyphenat} % disable all hyphenation
\setlength{\emergencystretch}{3em} % allow extra hfill, needed if hyphenation disabled
%\overfullrule=1mm % mark overfull boxes
%\usepackage{showframe} % show edges of text areas
% Page layout
\usepackage[left=15mm,right=15mm,top=15mm,bottom=20mm,
   nohead,foot=10mm]{geometry}
% Page headers
\usepackage{scrlayer-scrpage}
\usepackage{lastpage}
% Page header
\KOMAoptions{headsepline=0pt,plainheadsepline=off}
\ihead*{}
\chead*{}
\ohead*{}
% Page footer
\KOMAoptions{footsepline=0pt,plainfootsepline=off}
\ifoot*{}
\cfoot*{Page \thepage{} of \pageref*{LastPage}}
\ofoot*{}
% Text layout
\KOMAoption{parskip}{never}
\newlength{\myparindent}
\newlength{\myparskip}
\setlength{\myparindent}{0pt}
\setlength{\myparskip}{5pt plus 1pt}
\setparsizes{\myparindent}{\myparskip}{0.1\linewidth plus 1fil}
\RedeclareSectionCommand[beforeskip=6pt,afterskip=3pt,afterindent=false]{section}
\RedeclareSectionCommand[beforeskip=6pt,afterskip=-0.5em,afterindent=false]{paragraph}
\RaggedRight
% SVN metadata
\usepackage[today,revrange,nofancy]{svninfo}
\svnInfo $Id$
% Graphics
\usepackage{graphicx}
% Colour definitions
\usepackage{xcolor}
\definecolor{secondary}{HTML}{435584}
% Floats
\usepackage{subcaption}
% Listings
\usepackage{listings}
\lstset{language=C, basicstyle=\small\ttfamily,
   aboveskip=0pt, belowskip=0pt}
\usepackage{upquote} % to use correct glyphs for single-quote in verbatim
% SI units
\usepackage{siunitx}
\sisetup{per-mode = symbol, detect-all = true}
% Hyperlinks
\usepackage[
   colorlinks=true,allcolors=secondary,breaklinks=true,
   bookmarks=true,unicode=true,bookmarksopen,bookmarksnumbered]{hyperref}
% Document-specific settings
\renewcommand\abstractname{Executive Summary}

% Document details
\title{Design Brief: Group 1}
\author{
   Kevin Costner,
   Sean Connery,
   Charles Martin Smith,
   Andy Garcia,
   Richard Bradford
   }
\date{\svnMaxToday, Document v.\svnInfoMaxRevision}

\begin{document}

\maketitle

\abstract{%
   Write an executive summary for your project. This should not overflow into
   the next page, should not contain references, and should be readable by
   a wide audience.
   }

\section{Introduction}
Write an introduction, explaining the purpose and background of this project.
Give a brief description of the game to be implemented.
References to be cited like so \cite{stroustrup2000}.
Also include an overview of this document.

\section{System Design}

\section{Management}
Include a time plan.
Show task dependencies.
How are these going to be managed?

\section{Closure}

\bibliographystyle{ieeetr}
\bibliography{references}

\end{document}
